### 2008-12-19 talk/ecoop2009/rainbow.tex
A missing dot.

Promotion requires interleaving compile-time and run-time phases,
otherwise the compiler can only use information that is known ahead of
time. It is impossible in the "classical" approaches to partial
evaluation, in which the compiler always runs fully ahead of execution
This is a problem in many realistic use cases.  For example, in an
interpreter for a dynamic language, there is mostly no information
that can be clearly and statically used by the compiler before any
code has run.

>>>>

Promotion requires interleaving compile-time and run-time phases,
otherwise the compiler can only use information that is known ahead of
time. It is impossible in the "classical" approaches to partial
evaluation, in which the compiler always runs fully ahead of execution.
This is a problem in many realistic use cases.  For example, in an
interpreter for a dynamic language, there is mostly no information
that can be clearly and statically used by the compiler before any
code has run.
